Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-26 paper/paper.Rmd
Mods and Ethics section

Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, replication is not typically valued replication is not typically valued for publication [@makel2012], or in metrics of research productivity [@koole2012]. One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.

@@

**Add our own paragraph and IRB notes**

We are not familiar with the particularities of Institutional Review Boards across institutions, but suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.  We briefly highlight a few, with potential resolutions and comments.

*IRB approval is not possible within the time constraints of a class.*  To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine how to either 1) create a standard protocol that encompassses all replications that will be conducted (in which details can be later added and quickly approved), or 2) plan to submit the protocol early in the course, in line with IRB meeting schedules for quick turnarounds. Both issues may be simplified if the study or pool of studies to be replicated is pre-determined and if said studies provide full open-source materials that can be used in the IRB protocol submitted.

*There is a potential for harm given constraints of class.* Instructor review. Has been previously approved, and coercion/privacy confidentiality. Anonymizing codes; securing data. How much role instructors play in this dependent on student competence.

@@

## Funding and Power limitations

(Eric -I think this should be addressed - maybe mention free participant pools, value of learning how to recruit. OR if lucky (like us) apply for a grant.  Also call for OSF and other organizations devoted to replications to provide small grants of this sort.

Case-by-case selection

>>>>

Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, replication is not typically valued valued for publication [@makel2012], or in metrics of research productivity [@koole2012]. One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.

@@

In this set of replications, we opted for a case-by-case weighing of the costs and benefits of increasing power across all studies. Though we discussed these allocations and bartered allocations as a class, we had a few guiding principles. We first prioritized achieving the participants required for either 80% or original N (whichever was greater) for the maximum number of studies. This benefitted studies which were under the budget allocated for each individual project (i.e. studies that had large effect sizes and short participation times.)  Of those that achieved 80% power with sample sizes that were smaller than the original sample, we reduced the most expensive studies down to N required for 80% power. This allowed us to reach our budget goals with the exception of one particularly expensive study.  Fortunately, this student found external funding to reach 80% power. If this were not possible, we would have likely excluded this study from the pre-registration.

@@

Institutional Review Boards are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.  We address just two, with potential resolutions and comments.

Instructors may first be concerned that IRB approval is not possible within the time constraints of the class.  To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine how to either 1) create a standard protocol that encompassses all replications that will be conducted (in which details can be later added and quickly approved), or 2) plan to submit the protocol early in the course, in line with IRB meeting schedules for quick turnarounds. Both issues may be simplified if the study or pool of studies to be replicated is pre-determined and if these studies provide full open-source materials that can be used in the IRB protocol submitted.

In addition, instructors and review boards may believe there is a greater potential for harm given constraints of class. That is, there may be less oversight to each individual project.  However, we note that especially if the original studies have been previously approved by their respective institutional review board, the review process is similar to one might expect out of an advisee/advisor relationship. Particular consideration should be given to concerns of confidentiality of collected data, and we may suggest that for less experienced students, identifiable participant data should only be accessed by the instructor team.  Lastly, this project can also be a useful tool to have class discussions around coersion, harm vs. benefit, and other ethical issues that may arise during reserach.
